A Cloud Native Approach to Adversarial Robustness of Neural Networks

### 2024-08-16 main.tex
Updates from Overleaf

In the case of safety- or security-critical domains, considering the worst-case scenario is routine~\cite{sajid2013cloud}. Whether in the context of automotive safety~\cite{ai_automotive}, crytographic systems~\cite{leurent2020sha,kamal2017study}, or healthcare malpractice~\cite{ai_medical_imaging}, a component, algorithm, or system is considered broken if the \textit{failure rate} exceeds a certain amount, depending the risk to human life~\cite{iso26262}. An order of magnitude more automotive accidents, security breaches, or deaths due to negligence would be unacceptable and, as such, these standards are non-negotiable. However, this would mean testing many millions of samples for every model change that has the potential to injure a human, with orders of magnitude more stringent requirement in the case of potentially fatal systems. This is just not computationally feasible. Instead, researchers can use adversarial failure analysis~\cite{carlini_towards_2017,biggio_evasion_2013,meyers} to improve the precision of our estimates while only using a small set of test-data.

@@

We propose a methodology for model training and verification using accelerated failure-time (AFT) models, drawn from the field of \textit{survival analysis}. Additionally, since one goal is cost-efficiency, we restricted all of the experiments to a single one-thousand United States dollar research grant from Google.
AFT models are statistical models used to analyze multivariate effects on the observed failure rate to predict the time-to-failure across a wide variety of circumstances~\cite{aft_models,kleinbaum1996survival}. In medical science, these models are used to make claims like "smokers are twice as likely to die from lung cancer" or used to set the operating limits of manufactured components. This methodology can be used to map the relationship between various model tuning parameters and their effect on model performance.
The next section outlines the methodology for modelling the effect of model hyper-parameters during routine training procedures. We precisely outline the methodology for using survival analysis during the training of machine learning methods. 
% First, we present the proposed procedure in Algorithm~\ref{fig:alg} and a visual diagram of it in Figure~\ref{fig:experiments}. Then, in the sections below, we define accuracy (Section~\ref{acc}) and failure rate (Section~\ref{failure_rate}) in the context of survival analysis to make the concept of survival time clear (Section~\ref{survival_time}). We then discuss the importance of the ``acceleration assumption" (Section~\ref{accelerated}), the optimisation algorithm (Section~\ref{optimisation}), and the advantages of this approach (Section~\ref{advantages}).

\begin{algorithm}[h!]
    \caption{Survival Analysis for ML}
    \label{fig:alg}
\begin{algorithmic}
    \Require Samples $x$ of size $N$, model parameters $\theta$, loss function $L(y, \hat{y})$, classifier $K(x; \theta)$, and the number of trials, $n$, where the subscripts $t,i,a$ refer to the respective value for either the train, test, and/or attack sets, \textit{e.g.}, $N_t$ is size of the training set.
    \State Initialize classifier $K(x, \theta)$, training/inference/attack generation time arrays $T_t/T_i/T_a$, benign/adversarial accuracy arrays, $\lambda_{ben}/ \lambda_{adv}$
    \State $i = 0$
    \While{ $i < n$}
    \State \textbf{Initialize:} Random State, $R$ and split the classification data into the training set $x_t$ and the inference set $x_i$.
    \State \textbf{Optimise $L(y, \hat{y})$:} over $x_t, \theta$ according to some method (e.g Eq.~\ref{eq:sgd}) with a given batch size, $b$, and number of epochs, $m$.
    \State \textbf{Record:} $T_t[i] \gets$ Training Time.
    \State \textbf{Infer:}  $ \hat{y_i} = K(x_i, \theta) $.
    \State \textbf{Record:}  $ T_i[i] \gets $  Inference Time.
    \State \textbf{Calculate:}  $\lambda_{ben}[i] \gets $  Benign Accuracy (Eq.~\ref{eq:acc}).
    \State \textbf{Attack Generation: } find $x_a$ with Eq.~\ref{eq:fgm}.
    \State \textbf{Record:} $T_a[i] \gets$ attack generation time.
    \State \textbf{Infer:}  $ \hat{y}_a = K(x_a, \theta) $.
    \State \textbf{Calculate:}  $\lambda_{adv}[i] \gets $  Adversarial Accuracy (Eq.~\ref{eq:acc})
    \EndWhile
    \State \textbf{Fit AFT Model:} $S_{\theta}(T_a) \approx \phi N_a \cdot \lambda_{adv}$ with $\lambda_{ben}$, $T_t$, $T_i$, $m$, $b$, $R$ used as covariates to some acceleration factor, $\phi$ and  $N_a$ is the attack size array.
    \State \textbf{Return:} $S_{\theta}$
\end{algorithmic}
\end{algorithm}

@@

Accuracy measures the vulnerability or susceptibility of the model to noise-induced failures. A higher failure rate indicates a higher rate of misclassifications or incorrect predictions, signifying a weaker model in terms of \textit{robustness} against noise-induced failures. Throughout, we use the terminology \textit{benign accuracy} to refer to the performance on the test set using unperturbed data. The accuracy, $\lambda$, is defined as
\begin{equation}
    \lambda:= \mathrm{Accuracy} := 1 - \frac{\mathrm{False~Classifications}}{\mathrm{Total~Classifciations}},
    \label{eq:acc}
\end{equation}
which is generally assumed to indicate the rate of failures in real-world data sampled from the same distribution as the test data~\cite{tan2021critical}. However, the normal test/train split methodology consistently overestimates the model's performance in the presence of adversarial noise~\cite{croce_reliable_2020}. In addition, it ignores the run-time cost of a given architectural decision, caring only about accuracy on benchmark data~\cite{desislavov2021compute,bailly2022effects}. Additionally, it has been shown that it is trivial to generate adversarial counter examples that reveal the test/train split methodology to be optimistic at best~\cite{carlini_towards_2017,adversarialpatch,pixelattack,hopskipjump,biggio_poisoning_2013,chakraborty_adversarial_2018,dohmatob_generalized_2019,meyers}. We use $\lambda_{ben}$ to denote the accuracy on the unperturbed test data set $\lambda_{adv}$ to denote the accuracy on adversarial samples.

@@

The failure rate refers to the percentage or proportion of examples that cause the targeted ML model to misclassify or produce incorrect outputs~\cite{meyers}. To encompass the cost of a particular model or attack, the proposed methodology considers failures to be a function over some time interval (\textit{e.g.}, training time, inference time, attack generation time, \textit{etc.}) and some covariates, $\theta$, such that the failure rate is
\[
    h_{\theta}(t) :=  \frac{p(\textrm{False~Classification} \mid \theta)}{\Delta t} t,
\]
where $p(\textrm{False~Classification} \mid \theta)$ is the probability of a false classification given a particular set of hyper-parameters, $\theta$, $\Delta t$ is a time interval, and $t$ is a point in time. Note that  $1 - \text{Accuracy}$  is an estimate of this value when $\Delta t = t$ and converges to this value as the number of samples, $N \rightarrow \infty$. By re-parameterizing accuracy as a function of time, one can model the cost (measured in time) to performance (indicated by the number of failures) ratio with an accelerated failure time model.

@@

Accelerated failure rate models are widely used in industrial, medical, or risk-mitigation contexts~\cite{kleinbaum1996survival, aft_models} to model the effect of covariates on a model's expected time-to-failure (also called survival time. For industrial components, this often means testing the component under a variety  of extreme circumstances to induce failures prematurely. For medical applications, this is used to model the effect of demographic characteristics or the efficacy of certain treatments on a given disease. For machine learning, this means inducing failures during training to measure generalization performance.

The point of this is to model the \textit{survival time}, $S_{\theta}(t)$, as a function of the time, $t$,  and some set of model parameters, $\theta$ such that,
$$
    S_{\theta}(t) = p(T>t) = \exp\left(-\int_0^t h_{\theta}(u) \, du\right)
$$
where $p(T>t)$ is the probability that a model has not failed by time $t$ (``survives'' beyond time $t$). The expected survival time is
\[
	\mathbb{E}_{S_\theta}[T] = \int_0^{t^*}  S_\theta(t) \,dt,
\]
where $t^*$ is the latest time observed in the survival data. However, modelling $S_{\theta}(t)$ requires a choice in modelling function for $S_{\theta}$. The Log-Logistic, Log-Normal, and Weibull functions are widely used alternatives~\cite{kleinbaum1996survival}. For each trial, one can measure the inference time to define the time interval and the accuracy to estimate the number of failures in that time interval. This should be measured in both the benign and adversarial contexts. The full algorithm can be seen in Algorithm~\ref{fig:alg}.

@@

To choose a best-fit from the possible AFT functions, one should prepare the collected metrics and scores and then compare them using \textit{e.g.}, Akaike Information Criterion (AIC), Bayesian Information Criteria (BIC), or Concordance, as per the best-practices for this methodology~\cite{aft_models,kleinbaum1996survival}. For AIC and BIC, that means choosing the smallest value. Concordance, however, is a number between $0$ and $1$ that quantifies the degree to which the survival time is explained by the model, where a $1$ reflects a perfect explanation~\cite{kleinbaum1996survival} and 0.5 reflects random chance. By evaluating $\mathbb{E}_{S_\theta}[T]$ under extreme perturbations, one can test the model and minimize the number of evaluated samples~\cite{aft_models,kleinbaum1996survival} rather than relying on the $> 10^{12}$ samples as required by ISO26262~\cite{iso26262}. Other measures include the integrated calibration index (ICI) as well as the error at the median (E50)~\cite{ici}. These are the mean absolute difference between observed and predicted probabilities and the median absolute difference between observed and predicted probabilities, respectively~\cite{ici}. Then, one should plot all the expected and observed values for all three functions according to the method described by Austin \textit{et al.}~\cite{ici} (see Figure~\ref{fig:qq}) to visually inspect each model for goodness-of-fit. \cm{Additionally, we split the data into a training set that was used to fit the model (80\%) and an unseen test set (20\%) and measured the concordance, ICI, and E50 for each set.}

\subsubsection{\cm{The Advantages of AFT models}}
\cm{
}

@@

Using accelerated failure time models under adverse ones (accelerated failure time), $S_{adv}$. The survival time for is
$$
    S_{adv} := S(t_i; x, y, \theta) \mathrm{~~where~~} 0 < \varepsilon \leq \varepsilon_{max}.
$$
This can also be thought of in terms of the accelerated failure time assumption~\cite{kleinbaum1996survival}
\begin{equation} \label{assumption}
    S_{adv} \approx  \phi S_{ben}(\phi t),
\end{equation}
where $\phi$ is some acceleration factor described by the joint effect of the covariates. This assumption means we can evaluate the benign accuracy using a small number of adversarial samples~\cite{kleinbaum1996survival}, with our precision coming from careful time measurements rather than massive test sets.
However, in order to find the optimal hyper-parameter configurations for both the model and attack, one must search this space systematically.

@@

ML models are typically trained across a wide variety of hyper-parameters where each model is determined by minimizing an optimisation program (minimizing a loss function) associated with the machine learning problem. However, the number of hyper-parameter combinations are often infinite or at least exponential in the number of hyper-parameters,
making it infeasible to exhaustively evaluate the entire hyper-parameter search space. Additionally, the goals of test-set accuracy and adversarial accuracy are often at odds~\cite{carlini_towards_2017} --- with several researchers noting an inverse relationship between model accuracy and model robustness~\cite{carlini_towards_2017,meyers,dohmatob_generalized_2019}. Therefore, a proper search would keep this dual-objective in mind.
To optimise for adversarial and benign accuracy simultaneously, we propose the use of the Tree-structure Parzen Estimator (TPE) while converging over tens or hundreds of trials~\cite{ozaki2020multiobjective}.

\subsection{Advantages of this Methodology}
\label{advantages}

Because of the small number of samples needed for building AFT models (when compared to testing against massive in-distribution test sets), AFT models could, for example, act as a unit test in machine learning applications. This is in contrast to a full-system integration tests to evaluate changes to a single model, signal processing technique, data storage format, or API access mechanism~\cite{schmoor2000sample,lachin1981introduction}. It could also be used to highlight error-prone classes or other subsets of data to reduce error or create synthetic samples as is common in medical research~\cite{kleinbaum1996survival}. Furthermore, by isolating changes and testing them as quickly as possible, it is  easier to parse cause and effect when compared to full-system integration tests that could include many changes from many different development teams and require live and potentially dangerous systems (like cars, drones, or industrial equipment) to effectively test. To further increase development velocity, these models can quantify the marginal risk associated with each change, as dictated by the ISO 26262 standard~\cite{iso26262}. This risk analysis is outlined in the subsection below.

@@

In addition to the survival analysis, we can use an estimate of survival time to conduct a cost analysis as dictated by ISO26262~\cite{iso26262} which allows us to quantify the marginal risk. To quantify this marginal risk, one must measure the benign and adversarial accuracies (see Eqs.~\ref{eq:adv_success}~and~~\ref{eq:acc}), the model training time ($t_{t}$), the model inference time or latency ($t_{i}$), the attack generation time ($t_{a}$), the cost per hour for a particular hardware ($C$), as well as the power consumption ($P$) of each tested model and attack. The final subsection outlines why these metrics are important and their usage in this methodology.

@@

A successful attack is one that induces failure in a model. That is, the expected survival time, $\mathbb{E}_{S_\theta}[T]$, can be thought of as the average time it takes for an attacker to induce a change in the model output. We approximate this for each attack/defence configuration by the total attack time, $T_a$, for $n$ samples, $i$ iterations, and attack time per sample, $t_a$, as
\begin{equation}
    \label{attack_time}
    T_a := t_a \cdot n \cdot i.
\end{equation}
We restricted this to a single iteration such that $i =1$ as described in FGM~\cite{fgm}.

@@

Furthermore, we approach the cost of deployment at two scales. Firstly, we consider the cloud-rental scale, where a small-business might test and deploy a model, using \textit{e.g.}, the Google Cloud Platform\footnote{\href{https://cloud.google.com}{https://cloud.google.com}} (GCP) compute costs as a measure of total cost. However, at a certain scale, (\textit{e.g.}, to deploy a self-driving car) it is  more appropriate to talk about cost in terms of power. Finally, we define best-case and worst-case success metrics that provide an efficient way to minimize the latency, cost of deployment, and 
maximize the generalized performance of a model. We define the training cost as
$$
    C_t = C_h \cdot T_t,
    \label{eq:cost_training}
$$
the cost of model inference time as,
$$
    C_i = C_h \cdot T_i,
    \label{eq:cost_inference}
$$
and the cost of an attack as,
$$
    C_a = C_h \cdot T_a.
    \label{eq:cost_attack}
$$
where $C_h$ is the cost per unit time for the hardware, $T_t$ is the training time, $T_i$ is the inference time, and $T_a$ is the attack generation time, as defined above.

@@

In security analysis, it is  routine to think in optimistic terms for both the attacker and defender. In cryptography, these ideal attack- and defence-scenarios are used to test the computational feasibility of subverting a particular cryptographic system~\cite{kamal2017study,leurent2020sha} (\textit{e.g.}, whether or not a given cryptographic method should be considered ``broken"). For our purposes, by assuming the best-case scenario for both attacker and defender, we can model the Pareto front --- the best-case asymptotic behavior --- of either party~\cite{zitzler2008quality}.
As such, we center our analysis on the Fast Gradient Method~\cite{fgm} (see Eq.~\ref{eq:fgm}) which is both effective and fast~\cite{meyers}. If the cost to a model builder is much larger than the cost to an attacker ($C_t \gg C_a$), then it is  clear that the model is ``broken" in this cryptographic sense and can be discarded as ineffective.

@@

\subsection{Cloud Platform and Hardware}
To conduct the experiments and have access to different types of hardware, we utilized GCP. Six virtual machines running container optimised operating system provided by GCP constituted the test-bed. Using Google Kubernetes Engine 1.27.3 and Containerd 1.7.0, a cluster consisting of six worker nodes was created. Three worker nodes were responsible for running the monitoring platforms such as Prometheus 2.47.2 and Grafana 10.2.0. These nodes were of the ``e2-medium" instance type provided by GCP. In total, three GPU models were used--the Nvidia P100, V100, and L4. For P100 and V100 GPUs, the ``n1-standard-2'' type was used for the nodes and for L4 GPUs the ``g2-standard-4'' was used.

@@

For each hardware configuration and dataset, we ran one thousand trials, a number that should converge to a Pareto-optimal result~\cite{ozaki2020multiobjective,zitzler2008quality} for the TPE algorithm, within some expected error bounds~\cite{legriel2010approximating}. We used three optimisation criteria: benign accuracy, training time, and adversarial accuracy, seeking to maximize both benign and adversarial accuracy while minimizing training time (and therefore deployment cost). We selected a set of parameters as per the TPE algorithm and trained on 80\% of the samples. Of the remaining samples, 100 were withheld to be attacked and used to evaluate the adversarial accuracy. Figure~\ref{fig:experiments} illustrates this methodology. For each dataset, we tested this on ten random splits of the data. For each trial, we recorded attack generation time, model training time, model inference time, benign accuracy and adversarial accuracy, and the size of the training set, test set, and attack. Using these values, we fit an AFT model to the number of failures (indicated by accuracy and sample size) and the attack generation time after adding dummy variables for the dataset and hardware device. Additionally, we fit the function as described in Algorithm~\ref{fig:alg}.

@@

The evaluations were restricted to a single model. Primarily, this was done to meet the budgetary constraints since evaluating more models would mean evaluating fewer pieces of hardware. As discussed in Section~\ref{learning_rate}, the relationship between hardware specifications, model-size, data distribution, the optimal learning rate, the optimal batch size, and the optimal number of epochs is highly complex and hard to predict. So, we sampled learning rates $\in [10^{-6}, 1]$, batch sizes $\in [1, 10^5]$, and epochs $\in [1, 50]$ for MNIST and CIFAR10 on the P100 and V100. For CIFAR100, the range of the tested epochs was increased to be $\in [1, 100]$. The Feature Squeezing defence~\cite{feature_squeezing} was used to evaluate the efficacy of different bit-depths on the L4 hardware, as provided by IBM's adversarial robustness toolbox~\cite{art2018} with bit depths $\in [4,8,16,32,64]$ which casts the inputs into \texttt{Pytorch} compatible arrays. Model parameters were chosen using the \texttt{Optuna} optimisation framework, the configuration was handled by \texttt{hydra}, and \texttt{dvc} was used to ensure reproducibility and aid in collaborative development.

@@

This section presents and discusses the results for all of the experiments across all datasets and hardware. First, the measured data in Secs.~\ref{res:acc}-\ref{res:cost} are discussed, and then the fitted AFT model in Section~\ref{res:aft}.

>>>>

In the case of safety- or security-critical domains, considering the worst-case scenario is routine~\cite{sajid2013cloud}. Whether in the context of automotive safety~\cite{ai_automotive}, crytographic systems~\cite{leurent2020sha,kamal2017study}, or healthcare malpractice~\cite{ai_medical_imaging}, a component, algorithm, or system is considered broken if the \textit{failure rate} exceeds a certain amount, depending the risk to human life~\cite{IEC61508}. An order of magnitude more automotive accidents, security breaches, or deaths due to negligence would be unacceptable and, as such, these standards are non-negotiable. However, this would mean testing many millions of samples for every model change that has the potential to injure a human, with orders of magnitude more stringent requirement in the case of potentially fatal systems. This is just not computationally feasible. Instead, researchers can use adversarial failure analysis~\cite{carlini_towards_2017,biggio_evasion_2013,meyers} to improve the precision of our estimates while only using a small set of test-data.

@@

We propose a methodology for model training and verification using accelerated failure-time (AFT) models, drawn from the field of \textit{survival analysis}, with a focus on cost-efficient evaluation methods.
AFT models are statistical models used to analyze multivariate effects on the observed failure rate to predict the time-to-failure across a wide variety of circumstances~\cite{aft_models,kleinbaum1996survival}. In medical science, these models are used to make claims like ``smokers are twice as likely to die from lung cancer'' or used to set the operating limits of manufactured components. This methodology can be used to map the relationship between various model tuning parameters and their effect on model performance.
The next section outlines the methodology for modelling the effect of model hyper-parameters during routine training procedures. We precisely outline the methodology for using survival analysis during the training of machine learning methods. 
% First, we present the proposed procedure in Algorithm~\ref{fig:alg} and a visual diagram of it in Figure~\ref{fig:experiments}. Then, in the sections below, we define accuracy (Section~\ref{acc}) and failure rate (Section~\ref{failure_rate}) in the context of survival analysis to make the concept of survival time clear (Section~\ref{survival_time}). We then discuss the importance of the ``acceleration assumption" (Section~\ref{accelerated}), the optimisation algorithm (Section~\ref{optimisation}), and the advantages of this approach (Section~\ref{advantages}).

\begin{algorithm}[h!]
    \caption{Survival Analysis for ML}
    \label{fig:alg}
\begin{algorithmic}
    \Require Samples $x$ of size $N$, model parameters $\theta$, loss function $L(y, \hat{y})$, classifier $K(x; \theta)$, and the number of trials, $n$, where the subscripts $t,i,a$ refer to the respective value for either the train, test, and/or attack sets, \textit{e.g.}, $N_t$ is size of the training set.
    \State Initialize classifier $K(x, \theta)$, training/inference/attack generation time arrays $T_t/T_i/T_a$, benign/adversarial accuracy arrays, $\lambda_{ben}/ \lambda_{adv}$
    \State $i = 0$
    \While{ $i < n$}
    \State \textbf{Initialize:} Random State, $R$ and split the classification data into the training set $x_t$ and the inference set $x_i$.
    \State \textbf{Optimise $L(y, \hat{y})$:} over $x_t, \theta$ according to some method (e.g Eq.~\ref{eq:sgd}) with a given batch size, $b$, and number of epochs, $m$.
    \State  $T_t[i] \gets$ Training Time.
    \State  $ \hat{y_i} = K(x_i, \theta) $.
    \State  $ T_i[i] \gets $  Inference Time.
    \State  $\lambda_{ben}[i] \gets $  Benign Accuracy (Eq.~\ref{eq:acc}).
    \State find $x_a$ with Eq.~\ref{eq:fgm}.
    \State  $T_a[i] \gets$ attack generation time.
    \State  $ \hat{y}_a = K(x_a, \theta) $.
    \State  $\lambda_{adv}[i] \gets $  Adversarial Accuracy (Eq.~\ref{eq:acc})
    \EndWhile
    \State $S_{\theta}(T_a) \approx \phi N_a \cdot \lambda_{adv}$ with $\lambda_{ben}$, $T_t$, $T_i$, $m$, $b$, $R$ \\
    % used as covariates to some acceleration factor, $\phi$ and  $N_a$ is the attack size array.
    \Return $S_{\theta}$
\end{algorithmic}
\end{algorithm}

@@

Accuracy measures the vulnerability or susceptibility of the model to failures. A larger accurate indicates a higher rate of true classifications, signifying a weaker model in terms of \textit{robustness} against (noise-induced) failures. Throughout, we use the terminology \textit{benign} accuracy to refer to the performance on the test set using unperturbed data and \textit{adversarial} to refer to the performance in the presence of additive noise that is intended to confuse the model. The subscripts \textit{ben} and \textit{adv} are used respectively. The accuracy, $\lambda$, is defined as
\begin{equation}
    \lambda:= \mathrm{Accuracy} := 1 - \frac{\mathrm{False~Classifications}}{\mathrm{Total~Classifciations}},
    \label{eq:acc}
\end{equation}
which is generally assumed to indicate the rate of successes in real-world data sampled from the same distribution as the training data~\cite{tan2021critical}. However, the normal test/train split methodology consistently overestimates the model's performance in the presence of adversarial noise~\cite{croce_reliable_2020.
In addition, it ignores the run-time cost of a given architectural decision, caring only about accuracy on benchmark data~\cite{desislavov2021compute,bailly2022effects}. Additionally, it has been shown that it is trivial to generate adversarial counter examples that reveal the test/train split methodology to be optimistic at best~\cite{carlini_towards_2017,adversarialpatch,pixelattack,hopskipjump,biggio_poisoning_2013,chakraborty_adversarial_2018,dohmatob_generalized_2019,meyers}.

@@

The failure rate refers to the percentage or proportion of examples that cause the targeted ML model to misclassify or produce incorrect outputs~\cite{meyers}. To encompass the cost of a particular model or attack, the proposed methodology considers failures to be a function over some time interval (\textit{e.g.}, training time, inference time, attack generation time, \textit{etc.}) and some covariates, $\theta$, so that the failure rate is the average time until a failure in a time interval around time, $t$, such that:
\[
    h_{\theta}(t) :=  \frac{p(\textrm{False~Classification} \mid \theta)}{\Delta t} t,
\]
where $p(\textrm{False~Classification} \mid \theta)$ is the probability of a false classification given a particular set of hyper-parameters, $\theta$, $\Delta t$ is a time interval, and $t$ is a point in time.  Note that  $1 - \lambda$  is an estimate of this value when $\Delta t = t$ and converges to this value as the number of samples, $N \rightarrow \infty$. By modelling accuracy as a function of time, one can then compare the probability of failure to the cost, which is also measured in time, allowing one to make deployment decisions based on the risk analysis standards outlined in IEC61508~\cite{IEC61508}. This then allows us to make claims like ``increasing training time by X\% will yield survival time gains of Y\%''~\cite{meyers_aft}.

@@

AFT models are widely used in industrial, medical, or risk-mitigation contexts~\cite{kleinbaum1996survival, aft_models} to model the effect of covariates on a model's expected time-to-failure (also called survival time. For industrial components, this often means testing the component under a variety  of extreme circumstances to induce failures prematurely. For medical applications, this is used to model the effect of demographic characteristics or the efficacy of certain treatments on a given disease. For machine learning, this means inducing failures during training to measure generalization performance.

The point of this is to model the \textit{survival time}, $S_{\theta}(t)$, as a function of the time, $t$,  and some set of model parameters, $\theta$ such that,
$$
    S_{\theta}(t) = p(T>t) = \exp\left(-\int_0^t h_{\theta}(u) \, du\right)
$$
where $p(T>t)$ is the probability that a model has not failed by time $t$ (``survives'' beyond time $t$). The expected survival time is
\[
	\mathbb{E}_{S_\theta}[T] = \int_0^{t^*}  S_\theta(t) \,dt,
\]
where $t^*$ is the latest time observed in the survival data. However, modelling $S_{\theta}(t)$ requires a choice in modelling function for $S_{\theta}$. The Log-Logistic, Log-Normal, and Weibull functions are widely used alternatives~\cite{kleinbaum1996survival}. For each trial, one can measure the inference time to define the time interval and the accuracy to estimate the number of failures in that time interval. The full algorithm can be seen in Algorithm~\ref{fig:alg}.

@@

To choose a best-fit from the possible AFT functions, one should prepare the collected metrics and scores and then compare them using \textit{e.g.}, Akaike Information Criterion (AIC), Bayesian Information Criteria (BIC), or Concordance, as per the best-practices for this methodology~\cite{aft_models,kleinbaum1996survival}. For AIC and BIC, that means choosing the smallest value. Concordance, however, is a number between $0$ and $1$ that quantifies the degree to which the survival time is explained by the model, where a $1$ reflects a perfect explanation~\cite{kleinbaum1996survival} and 0.5 reflects random chance. By evaluating $\mathbb{E}_{S_\theta}[T]$ under extreme perturbations, one can test the model and minimize the number of evaluated samples~\cite{aft_models,kleinbaum1996survival} rather than relying on the $> 10^{12}$ samples as required by IEC61508~\cite{IEC61508}. We also noted the integrated calibration index (ICI) as well as the error at the median (E50)~\cite{ici}. These are the mean absolute difference between observed and predicted probabilities and the median absolute difference between observed and predicted probabilities, respectively~\cite{ici}. Then, the fitted AFT models were plotted using that compares the fitted AFT model to a cubic spline fit to the data~\textit{et al.}~\cite{ici}  to visually inspect each model for goodness-of-fit (see Figure~\ref{fig:qq}). \cm{Additionally, the data were split into a training set that was used to fit the model (80\%) and an unseen test set (20\%) and the concordance, ICI, and E50 were measured for both.}

@@

Using accelerated failure time models under adverse ones (accelerated failure time), $S_{adv}$. The survival time for is
$$
    S_{adv} := S(t_i; x, y, \theta) \mathrm{~~where~~} 0 < \varepsilon \leq \varepsilon_{max}.
$$
This can also be thought of in terms of the accelerated failure time assumption~\cite{kleinbaum1996survival}
\begin{equation} \label{assumption}
    S_\theta(t) = S_0 \left( \frac{t}{\phi_\theta(x)} \right)
\end{equation}
where $\phi$ is some acceleration factor described by the joint effect of the covariates and $S_0$ is the baseline hazard function (where the effect of the covariates are 0). This assumption means we can evaluate the generalization performance using a small number of adversarial samples~\cite{kleinbaum1996survival}, with our precision coming from careful time measurements rather than massive test sets.
However, in order to find the optimal hyper-parameter configurations for both the model and attack, one must search this space systematically.

@@

ML models are typically trained by examining the effect of the entire hyper-parameter space on the resulting accuracy. However, the number of hyper-parameter combinations are often infinite or at least exponential in the number of hyper-parameters,
making it infeasible to exhaustively evaluate the entire hyper-parameter search space. Additionally, the goals of test-set accuracy and adversarial accuracy are often at odds~\cite{carlini_towards_2017} --- with several researchers noting an inverse relationship between model accuracy and model robustness~\cite{carlini_towards_2017,meyers,dohmatob_generalized_2019}. Therefore, a proper search would keep this dual-objective in mind.
To optimise for adversarial and benign accuracy simultaneously, we propose the use of the Tree-structure Parzen Estimator (TPE) because it has been shown to converge  over tens or hundreds of trials rather the the 1000s of trials required by other multi-objective optimization algorithms like CMAES or NGSA-II~\cite{ozaki2020multiobjective,optuna,tpe_params}.

@@

In addition to the survival analysis, we can use an estimate of survival time to conduct a cost analysis as dictated by IEC61508~\cite{IEC61508} which allows us to quantify the marginal risk. To quantify this marginal risk, one must measure the benign and adversarial accuracies (see Eqs.~\ref{eq:adv_success}~and~~\ref{eq:acc}), the model training time ($t_{t}$), the model inference time or latency ($t_{i}$), the attack generation time ($t_{a}$), the cost per hour for a particular hardware ($C$), as well as the power consumption ($P$) of each tested model and attack.

@@

A successful attack is one that induces failure in a model. That is, the expected survival time, $\mathbb{E}_{S_\theta}[T]$, can be thought of as the average time it takes for an attacker to induce a change in the model output. We approximate this for each attack/defence configuration by the total attack time, $T_a$, for $n$ samples, $i$ iterations, and attack time per sample, $t_a$, as
\begin{equation}
    \label{attack_time}
    T_a := t_a \cdot n \cdot i.
\end{equation}
In the interest of time, our chosen attack, FGM, uses only a single iteration $i =1$~\cite{fgm}.

@@

Furthermore, we approach the cost of deployment at two scales. Firstly, we consider the cloud-rental scale, where a small-business might test and deploy a model using \textit{e.g.}, the Google Cloud Platform\footnote{\href{https://cloud.google.com}{https://cloud.google.com}} (GCP) compute costs as a measure of total cost. However, at a certain scale or with certain applications, it is  more appropriate to talk about cost in terms of power (\textit{e.g.}, to deploy a self-driving car with a useful operating range). Finally, we define best-case and worst-case success metrics that provide an efficient way to minimize the latency, cost of deployment, and 
maximize the generalized performance of a model. We define the training cost as
$$
    C_t = C_h \cdot T_t,
$$
the cost of model inference time as,
$$
    C_i = C_h \cdot T_i,
$$
and the cost of an attack as,
$$
    C_a = C_h \cdot T_a.
$$
where $C_h$ is the cost per unit time for the hardware, $T_t$ is the training time, $T_i$ is the inference time, and $T_a$ is the attack generation time, as defined above.

@@

In security analysis, it is  routine to think in optimistic terms for both the attacker and defender. In cryptography, these ideal attack- and defence-scenarios are used to test the computational feasibility of subverting a particular cryptographic system~\cite{kamal2017study,leurent2020sha} (\textit{e.g.}, whether or not a given cryptographic method should be considered ``broken"). Using AFTs, one can model the Pareto front --- the set of points that are superior to all others in the search space --- of either party~\cite{zitzler2008quality}. By using a whitebox attack to generate the failures, we ensure that our defender operates under the worst case scenario while the attacker operates under their best case scenario to yield a worst-case failure rate. As such, we center our analysis on the whitebox Fast Gradient Method~\cite{fgm} (see Eq.~\ref{eq:fgm}) which is both effective and fast~\cite{meyers}. If the cost to a model builder is much larger than the cost to an attacker ($C_t \gg C_a$), then it is  clear that the model is ``broken" in this cryptographic sense and can be discarded as ineffective.

@@

\subsection{Cloud Platform and Hardware}
To conduct the experiments and have access to different types of hardware, we utilized GCP. Six virtual machines running container optimised operating system provided by GCP constituted the test-bed. Using Google Kubernetes Engine 1.27.3 and Containerd 1.7.0, a cluster consisting of six worker nodes was created. Three worker nodes were responsible for running the monitoring platforms-- Prometheus 2.47.2 and Grafana 10.2.0. These nodes were of the ``e2-medium" instance type provided by GCP. In total, three GPU architectures were used--the Nvidia P100, V100, and L4. For P100 and V100 GPUs, the ``n1-standard-2'' type was used for the nodes and for L4 GPUs the ``g2-standard-4'' was used.

@@

For each hardware configuration and dataset, the TPE algorithm was used to select the hyper-parameters~\cite{ozaki2020multiobjective,zitzler2008quality}, and it was iterated for 1000 trials. This was chosen to be significantly larger than the 200 used successfully by Watanabe~\textit{et. al.}~\cite{tpe_params} while still allowing for reasonable run times. In reality, the correct number of iterations will be determined by the frequency of local minima across the search space and the number of optimisation criteria where marginally more minima or criteria require significantly more trials to yield accurate results~\cite{legriel2010approximating}. Examining the effect of this and other TPE parameters on the total run-time and performance of this methodology was outside the scope of this work.
We used three optimisation criteria: benign accuracy, training time, and adversarial accuracy, seeking to maximize both benign and adversarial accuracy while minimizing training time (and therefore deployment cost). We selected a set of parameters as per the TPE algorithm and trained on 80\% of the samples for each of the MNIST, CIFAR10, and CIFAR100 datasets. Of the remaining samples, 100 were withheld to be attacked and used to evaluate the adversarial accuracy. Figure~\ref{fig:experiments} illustrates this methodology. For each dataset, we tested this on ten random splits of the data to create 10 unique test/train pairs. For each trial, we recorded attack generation time, model training time, model inference time, benign accuracy and adversarial accuracy, and the size of the training set, test set, and attack set. Using these values, we fit an AFT model to the number of failures (indicated by accuracy and sample size) and the attack generation time after adding dummy variables for the dataset and hardware device. Additionally, we approximate the AFT model using the methodology described in Algorithm~\ref{fig:alg}.

@@

The evaluations were restricted to a single model. Primarily, this was done to meet the budgetary constraints since evaluating more models would mean evaluating fewer pieces of hardware. As discussed in Section~\ref{learning_rate}, the relationship between hardware specifications, hyper-parameters, and performance is highly complex and hard to predict. So, we sampled learning rates $\in [10^{-6}, 1]$, batch sizes $\in [1, 10^5]$, and epochs $\in [1, 50]$ for MNIST and CIFAR10 on the P100 and V100. For CIFAR100, the range of the tested epochs was increased to be $\in [1, 100]$. The Feature Squeezing defence~\cite{feature_squeezing} was used to evaluate the efficacy of different bit-depths on the L4 hardware, as provided by IBM's adversarial robustness toolbox~\cite{art2018} with bit depths $\in [4,8,16,32,64]$ which casts the inputs into \texttt{pytorch} compatible arrays. Model parameters were chosen using the \texttt{optuna} optimisation framework, the configuration was handled by \texttt{hydra}, and \texttt{dvc} was used to ensure reproducibility and aid in collaborative development.

@@

This section presents and discusses the results for all of the experiments across all datasets and hardware. First, the accuracy, training time, inference, and monetary cost are discussed in Secs.~\ref{res:acc}-\ref{res:cost}, followed by the fitted AFT model in Section~\ref{res:aft}.
